%-----------------------------------------
% Alex Hardwicke
% CV
%
% URL: http://github.com/mdwrigh2/resume
% This document is covered under the Creative Commons Attribution 3.0 Unported License
%-----------------------------------------

%!TEX TS-program = lualatex
%!TEX encoding = UTF-8 Unicode

\documentclass[11pt,a4paper,final]{moderncv}
\usepackage{fontspec}
\moderncvtheme[blue]{classic}

% DOCUMENT LAYOUT
\usepackage[scale=0.88]{geometry}
\setlength{\hintscolumnwidth}{20mm}
\AtBeginDocument{\recomputelengths}
% FONTS
\usepackage[latin1]{inputenc}
\defaultfontfeatures{Mapping=tex-text} % converts LaTeX specials (``quotes'' --- dashes etc.) to unicode

% Remove % to set to different fonts
%\setromanfont [Ligatures={Common},Numbers={OldStyle}]{Adobe Caslon Pro}
%\setmonofont[Scale=0.8]{Monaco}

% ---- CUSTOM AMPERSAND
\newcommand{\amper}{{\fontspec[Scale=.95]{Adobe Caslon Pro}\selectfont\itshape\&}}

% ---- MARGIN YEARS
%\newcommand{\years}[1]{\marginpar{\scriptsize #1}}


% PDF SETUP
% ---- FILL IN HERE THE DOC TITLE AND AUTHOR


% Personal Information
\firstname{Alexander}
\familyname{Hardwicke}
\address{Magistratsvägen 17D}{226 43 Lund}
\mobile{0762 480546}
\email{alex.hardwicke@outlook.com}
\homepage{www.alexhardwicke.com}

\title{Alex Hardwicke's CV}

\nopagenumbers{}

\begin{document}

\maketitle

\section{Education}
    \cventry{Sep. 2011\\-- June 2014}{Computer Science}{}{Malmö University}{Malmö, Sweden}{
    Top grades in all courses (ECTS Grade A / Swedish VG / UK 1st)\newline
    My dissertation was about profiling the performance of multi-threaded applications, and what impacts that profiling can have. As part of this, I worked on further development of a profiling tool called CodeProbe.}

\section{Computer Skills}
    \cvline{Expert:}{C\#/.NET, WinRT, Windows Phone, Java, Android}
    \cvline{Skilled:}{ASP.NET, F\#, Git, JavaScript, SQL}
    \cvline{Interests:}{TypeScript}

\section{Experience}
    \cventry{Oct. 2014\\-- present}{Software Developer}{Erisma}{Malmö, Sweden}{}{
        \begin{itemize}% \itemsep -2pt % reduce space between items
            \item Worked on Mobigo Desktop software, using C\# and C++.
            \item Worked on Mobigo Mobile, using ASP.NET and JavaScript.
        \end{itemize}
    }
    \cventry{Aug. 2014\\-- Oct. 2014}{Teacher}{Edument}{Malmö, Sweden}{}{
        \begin{itemize}% \itemsep -2pt % reduce space between items
            \item Authored two intensive Java courses, at beginner and intermediate level.
            \item Taught git.
        \end{itemize}
    }
    \cventry{Sep. 2012\\-- Mar. 2014}{Teaching Assistant}{Malmö University}{Malmö, Sweden}{}{
        \begin{itemize}% \itemsep -2pt % reduce space between items
            \item Assisted first years reading Computer Science.
            \item Assisted first years reading Electrical Engineering.
            \item Assisted second and third years (my own classmates) reading Android Development.
        \end{itemize}
    }

\section{Personal Projects}
    \cventry{Dec. 2013}{Surge}{Remote Controller for Transmission}{Windows 8 Modern App}{C\#}{
        \begin{itemize}% \itemsep -2pt % reduce space between items
            \item Over 20000 downloads.
            \item Consistently good reviews, particularly about the UI and performance.
            \item More details available at \url{http://www.alexhardwicke.com/surge}
            \item Available at \url{http://apps.microsoft.com/windows/app/surge/97e772a6-62ff-4921-9cbf-44f9ec186037} \newline
        \end{itemize}
    }
    \cventry{June 2012}{Promenade}{Walk Tracker}{Android App}{Java}{
        \begin{itemize}% \itemsep -2pt % reduce space between items
            \item My first large mobile app, which I wrote to learn both Android development and app development in general.
            \item More details available at \url{http://www.alexhardwicke.com/promenade}
            \item Open sourced. Code available at \url{https://github.com/alexhardwicke/promenade}
            \item Available at \url{https://play.google.com/store/apps/details?id=com.digitalpies.promenade}
        \end{itemize}
    }

\section{Merits \& Certificates}
    \cventry{}{Parallel and Asynchronous Programming in C\# 5}{Edument}{}{}{}

\newpage

\section{Notable Achievements}
    \cvlistitem{Only undergraduate skilled enough to be an Android TA to final year students.}
    \cvlistitem{Read Computer Science in a foreign language and still had top grades in all courses.}
    \cvlistitem{Created an Arduino GPS tracker that communicates with an Android app using SMS and 3G.}

\section{About Me}
    \cvlistitem{I'm a new father.}
    \cvlistitem{I'm a hobby painter.}
    \cvlistitem{I'm a keen amateur photographer.}
    \cvlistitem{I'm a native speaker of English and am fluent in Swedish.}

\section{Extra}
    \cvlistitem{Fledgling StackOverflow contributor: \url{http://stackoverflow.com/users/2079472/alex-hardwicke}}

\section{References}
    \cvline{}{Available upon request.}

\section{Grades}
    \cvline{}{Available upon request.}
\end{document}